Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-24 surfaces-write-up/surface-write-up.tex
changes to section 4

\begin{thm}
\label{proj-generators-relations-intro}
Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let
$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$
for all $i$; suppose $\deg(f_i) = a_i$. 
Then $R_D$ is generated in degree at most 
\[
	\sum_{i=1}^n \ell_i a_i
\]
with relations generated in degree at most
\[
	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
\]
\end{thm}

@@

\begin{thm}
\label{lem:hirz-generators-relations}
Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  
Let $C_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further 
suppose $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.
Then $R_D$ is generated in degree less than 
\[
	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
	\sum_{\substack{i	\in \Tp(D) \\	j \in \Tm(D)}} (\bida_i
	\bidb_j - \bida_j \bidb_i)\ell_{i,j}
\]

@@

@@

\todo{Aaron: Give some definitions to make clear what the structure of divisors are}
\todo{Aaron: clarify that $R_D$ is assumed to have both positive bidegrees}
\todo{Aaron: Have $\ell_{i,j}$ been defined?}
Let $D = \sum_{i = 1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di (\hirz_m)$ such
that $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)
, (1,0), (0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch
surfaces before this paragraph; especially, describe what it's sections look
like.}

@@

@@

By Proposition ~\ref{prop:cone-generation}, in order to determining a spanning
set for $(R_D)_d,$ it suffices to find the extremal rays of $\Sigma.$
To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
We first consider the sub-cone $\Sigma_1 \subset \Sigma$
given by
\begin{align*}
	\Sigma_1 = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge -
d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i (\bida_i+\bidb_i) = 0
\}.	
\end{align*}
Then, $\Sigma_1$
has extremal rays given by

@@

Let $\Delta^{n-1}$ be the simplex with vertices $e_1, \ldots e_n$.
We can intersect $\Delta^{n-1}$ with the hyperplane $H$ given by
$\sum_{i=1}^n \bida_i X_i = 0$  to get a subspace $S \subseteq \Delta
^{n-1}$.  Since $\Sigma \subseteq S$, if each extremal rays of $S$ contains an element of the lattice $\Sigma$, then those representatives in $\Sigma$ are in fact the extremal rays of $\Sigma$.

The extremal rays of $S$ must lie on the edges of $\Delta
^{n - 1}$, \todo{Peter: Do we need to cite/argue this, or is it clear?}
and are given by the $e_i$'s
contained in $H$ and the intersection points $e_{i, j}$ of $H$
together with the edges $\overline{e_i e_j}$ of the simplex between
distinct $e_i, e_j$ not contained in $H$.
\todo{more detail above;  Peter: resolved?}
The following are elements of $R_D$ whose corresponding lattice point lies on each of the above extremal rays:

For $i \in \Te(D)$, define \todo{below section needs to be simplified, maybe
by introducing new variables}
\begin{equation}\label{eqn:epsilon_i}
	\epsilon_i := \left(\prod_{k \ne i} f_k^{-\alpha_k \ell_i \gcd(\bida_i, \bidb_i)}\right)
	(f_i^{\ell_i \frac{\gcd(\bida_i, \bidb_i)}{\bida_i + \bidb_i}\sum_{k \ne i}
	\alpha_k (\bida_k + \bidb_k)}) \in H^0(\ell_i \gcd(\bida_i, \bidb_i) D).
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, define
\begin{equation}\label{eqn:epsilon_i,j}
	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k \ell_{i,j} (\bida_i \bidb_
	j - \bida_j \bidb_i)} \right){f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i, j}
	(\bida_i \bidb_j - \bida_j \bidb_i) D)
\end{equation}

\noindent
where
\[
	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
	\alpha_k \bidb_k = b_j (\alpha_i a_i + \alpha_j a_j) - a_j (\alpha_i b_i + \alpha_j b_j)
\]

\noindent
and
\[
	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
	\alpha_k \bidb_k = -b_i (\alpha_i a_i + \alpha_j a_j) + a_i (\alpha_i b_i + \alpha_j b_j).
\]
\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We don't use the $\epsilon$ here, and we do use the $e$ here.}
A quick calculation deduces that these $\epsilon_i$'s and $\epsilon_{i,j}$'s lie on the extremal rays given by the $e_i$'s and $e_{i,j}$'s.

Thus Proposition ~\ref{prop:cone-generation} implies that $R_D$ is generated in 
degrees less than the sum of the degrees of the $\epsilon_i$'s and $\epsilon_{i,j}$'s, which is
\[
	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{\substack{
	i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
\]
\todo{Aaron: Do you use $\sigma$ later? We are usually reserving $\sigma$ for a
lattice point. Perhaps something like $\delta$ would be more appropriate if you
want to refer to it later. Also, you should number if if you want to refer to
it later. In general, it's bad style to define things in the proofs. This could
have been defined prior to the theorem statement as well, which would simplify
the statement. We should also then clarify that $\sigma$ depends on $D$.  \\
Peter: $\sigma$ replaced by $\rho$. It's also defined now in the lemma statement rather than its proof.  
}

@@

\begin{lem}
$\ker(\psi)$ is generated in less than
\[
	\tau : = \rho
	+ \max \left(\max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
	i \in	\Tp \\ j\in \Tm}} (\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
	\right).
\]
\end{lem}

\begin{proof}
We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n\in \bk[z_1, z_2, z_3, z_4]$
 such that $\psi$ has relations of the form
\begin{equation}
\label{eqn:hirz-relations-psi}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

\noindent
whenever there is some degree $d \in \mathbb{N}$
and $c_i \ge -\alpha_i d$ satisfying $\bida_i + \sum_{j = 1}
^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.

To find such a $\beta_i$,
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$. \todo{Add $\ell_i$ defenition}

%Note that we can view a relation from Equation
%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
Let $\Sigma'\subseteq \Sigma$ be the \todo{change all $S$ to sigma's}
set
\begin{align*}
	\Sigma' = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
= 0 \}
\end{align*}

Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \br$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \br$
Then a careful computation deduces that 
%if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
	\sigma = \lambda + E
\end{equation}
where $\lambda \in \Sigma$ and
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \br, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \br, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}

@@

\noindent
which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$.
We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
\[
	\deg(F) = \deg(E) \le \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm \end{cases}.
\]

@@

\noindent
where
\[
	\tau = \sigma
	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
\]
\end{thm}
\todo{Aaron: Shouldn't $\tau$ not include $\sigma$?  Peter: Fixed}

\todo{Aaron: I know exactly what is going on, but please spell out the proof in 2 lines for completeness.}

@@

Fortunately, the Picard group of $X$ blown up at a point is the same as that of
$X$ times an additional copy of $\bz$.  Perhaps analyzing the argument from
Lemma ~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma
and not the theorem with the same name} in the case of $\hirz_k$ from the
perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by
the blowup, might suggest a general method for blowups.

Answering Question ~\ref{qn:general-blowup} would in fact provide an answer for
all rational surfaces, via the minimal model program for surfaces
\todo{Reference}.  One might to provide an analogous result to Lemma
~\ref{lem:hirz-generators-relations} \todo{make sure this is the lemma and not
the theorem with the same name} in the case of all minimal surfaces:
\begin{question}
\label{qn:general-minimal-surface}
Can we describe generators and relations of $R_D$ for $D$ a divisor on an
arbitrary minimal surface $X$?
\end{question}

>>>>

\begin{thm}
\label{thm:proj-generators-relations-intro}
Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\mathbb{P}^m$.  Let
$f_i$ be homogeneous polynomials in $x_0, \ldots, x_m$ such that $C_i = v(f_i)$
for all $i$; suppose $\deg(f_i) = a_i$. 
Then $R_D$ is generated in degree at most 
\[
	\sum_{i=1}^n \ell_i a_i
\]
with relations generated in degree at most
\[
	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
\]
\end{thm}

@@

\begin{thm}
\label{thm:hirz-generators-relations}
Let $D = \sum_{i=1}^n \alpha_i C_i$ for curves $C_i$ on $\hirz_k$.  
Let $C_i = V(f_i)$ where $f_i \in \sco(a_i, b_i)$; further 
suppose $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.
Then $R_D$ is generated in degree less than 
\[
	\sigma = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i +
	\sum_{\substack{i	\in \Tp(D) \\	j \in \Tm(D)}} (\bida_i
	\bidb_j - \bida_j \bidb_i)\ell_{i,j}
\]

@@

\begin{defn}\label{def:ell_i}
Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$. \todo{Peter: better notation for fraction?}  Then notate
\[\ell_i = \lcm_{j\ne i}(k_i).\]
\end{defn}

@@

We can talk about sections of $\hirz_m$ in terms of polynomials in $u,v, w,x$; furthermore we can talk about bi-degrees of a monomial $u^a v^{b} w^c x^d$ given by $(a + b + mc, c + d)$.  Sections on open subsets of $\hirz_m$ look like polynomials with each monomial having the same bidegrees, and rational sections have both bidegrees 0. \todo{Peter @ Aaron: can you add your exact sequence argument for why this is true?}

Why can write $\bq$-divisors of $\hirz_m$ as $D = \sum_{i = 1}^n \alpha_i D_i \in \mathbb{Q} \otimes \di (\hirz_m)$, where each $D_i = V(f_i)$ for some polynomial $f_i$, with each monomial having the same bidegrees.  Since sections on $H^0(dD)$ must be rational sections, they must have both bidegrees non-negative, meaning that both bidegrees of $D$ must be non-negative for $R_D$ to be non-trivial.

For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are distinct divisors with bi-degrees $(1,0)$
, $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$. \todo{Talk a little about Hirzebruch
surfaces before this paragraph; especially, describe what it's sections look
like. \\
Peter: Fixed?
}

@@

\begin{defn}\label{def:ell_ij}
Let $D = \sum_{i=1}^n \alpha_i D_i$ where $\alpha_i = \frac{c_i}{k_i}$. \todo{Peter: better notation for fraction?}  Then notate
\[\ell_{i,j} = \lcm_{h\ne i,j}(k_h).\]
\end{defn}

@@

In order to determine a generating
set for $(R_D)_d,$ it suffices to find the extremal rays of $\Sigma.$
To do this, we extend the method of O'Dorney \cite[Theorem 8]{dorney:canonical}. 
We first consider the sub-cone $\Sigma_1 \subset \Sigma$
given by
\begin{align*}
	\Sigma_1 = \{ (d, c_1, \ldots, c_n) \in \bz_{\geq 0}^{n+1} : c_i \ge -
d \alpha_i \text{ for all }i \text{ and }\sum_{i=1}^n c_i (\bida_i+\bidb_i) = 0
\},
\end{align*}
which
has extremal rays given by

@@

Let $S$ be the $\mathbb{R}_{\ge 0}$ span of $e_1, \ldots e_n$.
We can intersect $S$ with the hyperplane $H$ given by
$\sum_{i=1}^n \bida_i X_i = 0$  to get a subspace $S' \subseteq S$.  Then, as long as each extremal rays of $S'$ contains an element of the lattice $\Sigma$, those representatives must in fact the extremal rays of $\Sigma'$.

The extremal rays of $S'$ can be represented by points lying only on the edges of 
$\overline{e_i e_j}$
and are given by the $e_i$'s
contained in $H$ and the intersection points $e_{i, j}$ of $H$
together with the edges $\overline{e_i e_j}$ of the simplex between
distinct $e_i, e_j$ not contained in $H$.
\todo{more detail above;  Peter: resolved?}
The following are elements of $R_D$ correspond to lattice point on each of the extremal rays listed above:

For $i \in \Te(D)$, define $\epsilon_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
\todo{below section needs to be simplified, maybe
by introducing new variables; 
Peter: I replaced some terms with degrees $d_i$ and $d_{i,j}$}
\begin{equation}\label{eqn:epsilon_i}
	\epsilon_i := \left(\prod_{k \ne i} f_k^{-\alpha_k d_i}\right)
	f_i^{ \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
	\alpha_k (\bida_k + \bidb_k)}.
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $\epsilon_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
\begin{equation}\label{eqn:epsilon_i,j}
	\epsilon_{i, j} := \left(\prod_{k \ne i, j} f_k^{-\alpha_k d_{i,j}} \right){f_i}^{s_1} {f_j}^{s_2}
\end{equation}

\noindent
where
\[
	s_1 = \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
	\alpha_k \bidb_k
\]

\noindent
and
\[
	s_2 = -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
	\alpha_k \bidb_k.
\]
\todo{Aaron: Why are $\epsilon_{i,j}$ defined here instead of $e_{i,j}$. We don't use the $\epsilon$ here, and we do use the $e$ here. \\
Peter: I have a slight leaning towards this notation, because the algebraic object is use more later (I think, although I'll check to make sure); also, I think writing out the ordered tuple would actually be harder, because there is no product notation, and it can be hard to denote the cordinates.}
A quick calculation deduces that these $\epsilon_i$'s and $\epsilon_{i,j}$'s lie on the extremal rays represented by the $e_i$'s and $e_{i,j}$'s, respectively.
\begin{rem}
For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a (possibly) different representative of it's extremal ray say that their lattice points correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
\end{rem}\todo{Peter: I don't like having a remark inside of a proof.  Also, it feels like this could reasonably be replaced with a better constructed/organized proof, so that $e_i$'s are just defined this way initially; let me know if you see a good way to do so...  As for Aaron's comment above, we could do something like that, except we already defined $e_i$'s to be something different, which might be equally/more confusing.}

Thus,
Proposition ~\ref{prop:cone-generation} implies that 
$R_D$ is generated in 
degrees less than the sum of the degrees of the $\epsilon_i$'s and $\epsilon_{i,j}$'s, which is
\[
	\rho = \sum_{i\in \Te(D)} \gcd(\bida_i, \bidb_i)\ell_i + \sum_{\substack{
	i \in \Tp(D) \\	j \in \Tm(D)}} (\bida_i \bidb_j- \bida_j \bidb_i)\ell_{i,j}.
\]
\todo{Aaron: Do you use $\sigma$ later? We are usually reserving $\sigma$ for a
lattice point. Perhaps something like $\delta$ would be more appropriate if you
want to refer to it later. Also, you should number if if you want to refer to
it later. In general, it's bad style to define things in the proofs. This could
have been defined prior to the theorem statement as well, which would simplify
the statement. We should also then clarify that $\sigma$ depends on $D$.  \\
Peter: $\sigma$ replaced by $\rho$. It's also defined now in the lemma statement rather than its proof.  
}

@@

\begin{lem}
$\ker(\psi)$ is generated in degrees less than
\[
	\tau : = \rho
	+ \max \left(\max_{i\in \Te}(\ell_i \gcd(a_i, b_i)), \max_{\substack{
	i \in	\Tp \\ j\in \Tm}} (\ell_{i,j} (\bida_i \bidb_j - \bida_j \bidb_i))
	\right).
\]
\end{lem}

\begin{proof}
We first claim that there exist $\beta_1, \ldots, \beta_n\in \bk[z_1, z_2, z_3, z_4]$
 such that $\ker(\psi)$ has relations of the form
\begin{equation}
\label{eqn:hirz-relations-psi}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

\noindent
whenever there is some degree $d \in \mathbb{N}$
and $c_j \ge -\alpha_j d$ (for all $j$) satisfying $\bida_i + \sum_{j = 1}
^n \bida_j c_j = 0$ and $\bidb_i + \sum_{j=1}^n \bidb_j c_j = 0$.

To find such a $\beta_i$,
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$.

%Note that we can view a relation from Equation
%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
Let $\Omega\subseteq \Sigma$ be the 
set
\begin{align*}
	\Omega = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
= 0 \}
\end{align*}

Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \br$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \br$
Then a careful computation deduces that 
%if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
	\sigma = \lambda + E
\end{equation}
where $\lambda \in \Sigma$ and
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \br, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \br, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}

@@

\noindent
which divides $(z_i - \beta_i) \prod_{i = 1}^n y_i^{c_i}$ (recall that $\rho$, defined in Equation \ref{eqn:def-sigma}, is an upper bound for generation degree).
We can bound $\deg(F)$ (which equals $\deg(F_\mu)$ for all $\mu$) by
\[
	\deg(F) = \deg(E) \le \begin{cases}
	\ell_i \gcd(\bida_i, \bidb_i)	&\mbox{ if } i \in \Te \\
	\max_{j \in \Tm} \bigl(\ell_{i, j} (\bida_i \bidb_j - \bida_j \bidb_i)\bigr)
	&\mbox{ if } i \in \Tp \\
	\max_{j \in \Tp} \bigl(\ell_{j, i} (\bida_j \bidb_ i - \bida_i \bidb_j) \bigr)
	&\mbox{ if } i \in \Tm \end{cases}.
\]

@@

\noindent
where
\[
	\tau = \sigma
	+ \max \left( \max_{i\in \Te} \bigl(\ell_i \gcd(a_i, b_i) \bigr),
	\max_{\substack{i \in \Tp \\ j \in \Tm}} \bigl(\ell_{i, j}
	(\bida_i \bidb_j - \bida_j \bidb_i) \bigr) \right).
\]
\end{thm}
\begin{proof}
The generation degree bound is as stated in Lemma \ref{lem:hirz-generators}.  By Proposition \ref{lem:composite-map}, the degree of generation of $\ker(\phi)$ is at most the maximum of the generation degrees of $\ker(\chi)$ and $\ker(\psi)$, giving us the desired relations bound.
\end{proof}

\todo{Aaron: Shouldn't $\tau$ not include $\sigma$?  Peter: Fixed}

\todo{Aaron: I know exactly what is going on, but please spell out the proof in 2 lines for completeness.\\
Peter: Better?}

@@

Fortunately, the Picard group of $X$ blown up at a point is the same as that of
$X$ times an additional copy of $\bz$.  Perhaps analyzing the argument from
Lemma ~\ref{thm:hirz-generators-relations} in the case of $\hirz_1$ from the
perspective of adding a copy of $\mathbb{Z}$ to the Picard group, as induced by
the blowup, might suggest a general method for blowups.

Answering Question ~\ref{qn:general-blowup} would in fact provide an answer for
all rational surfaces, via the minimal model program for surfaces
\todo{Reference}.  One might then hope to further extend these results to all minimal surfaces:
\begin{question}
\label{qn:general-minimal-surface}
Can we describe generators and relations of $R_D$ for $D$ a divisor on an
arbitrary minimal surface $X$?
\end{question}
